Estimating SARS-CoV-2 transmission in England from randomly sampled prevalence surveys

### 2024-03-12 introduction.tex

Typically, the core of an observation model is a \emph{convolution equation} or an approximation of it.
This equation links an observation at time $t$, $y_t$, to the incidence prior to time $t$.
In discrete time, it is:
\begin{align}
    y_t &= \zeta \sum_{i=0}^\infty I(t-i) f(i)
\end{align}
where $I(t)$ is the incidence at time $t$; $\zeta$ is the proportion of infections that are ever observed; and $f(i)$ is the probability that an infection at time $t-i$ is observed at time $t$, conditional on it ever being observed.

@@

\subsection{Data for estimating incidence and transmission} \label{intro:sec:data-for-estimating}

>>>>

Typically, the core of an observation model is a \emph{convolution equation} or an approximation of it.
This equation links the expectation of an observation at time $t$, $y_t$, conditional on the incidence prior to time $t$.
In discrete time, it is:
\begin{align}
    y_t &= \zeta \sum_{i=0}^\infty I(t-i) f(i)
\end{align}
where $I(t)$ is the incidence at time $t$; $\zeta$ is the proportion of infections that are ever observed; and $f(i)$ is the probability that an infection at time $t-i$ is observed at time $t$, conditional on it ever being observed.

@@

In this case we needed...

Urgency of situtation (cf HIV/AIDS) - rate of harm .

Needed rapid use of ideas

\subsection{Surveillance data} \label{intro:sec:data-for-estimating}
